
\chapter{Introduction}

Humanoid robots are robots designed to resemble the human body and behavior. They have the capability to perform a wide range of tasks and can be used in various fields such as entertainment, education, research, and medical care. The future use of humanoid robots is expected to expand as technology advances and they become more advanced in terms of their movements and cognitive abilities.

Humanoid robots have the potential to revolutionize the way we live and work. They can assist with dangerous or tedious tasks, and provide new opportunities for social and emotional interaction. In the future, humanoid robots could also play a significant role in fields such as healthcare, education, and entertainment, providing new and innovative solutions for many challenges.

ARMAREST aims to contribute to the development of humanoid robots by providing an interface for external communication and control, based on REST, which can be used to inspect and/or change the configuration of the robot. By creating a user-friendly and flexible interface, ARMAREST will help colleagues from \hht in their journey of creating better robots and pushing boundaries of robotic.

This implementation report consists of:
\begin{itemize}
    \item Changes to the Design: This chapter details any changes made to the design of the project during its development, including any modifications made to the original design draft.
    \item Degree of Implementation of Hard and Soft Requirements: This chapter examines the degree of implementation of both the hard and soft requirements for the project, including any limitations or challenges encountered during the development process.
    \item Organization of the Implementation: This chapter outlines how the team organized the work and divided tasks during the development of ARMAREST.
\item Overview of Unit Tests: This chapter provides an overview of the unit tests, that will be performed on ARMAREST, including the results and any issues encountered during testing. Note that core is tested as part of the launchtestserver launcher.
    \item Glossary: This chapter contains a list of terms used throughout the report, including definitions of technical terms and acronyms used in the project.
\end{itemize}
